Report on laboratory assignments 1 and 2 for EDA282, \\ Parallel Computer Organization and Design

### 2014-10-30 lab/report/include/lab2.tex
corrections

\subsection{Task 4}
To add the Owner (O) state to the existing MESI CCP, only small changes are needed. In \textit{readLine()} and \textit{writeRemoteAction()} no changes are needed. Turning to \textit{readRemoteAction()}, transitions from the E, M, and O states to the O state are added, and all of these transitions provide data to the calling cache. The action taken when in the shared state is removed. For \textit{writeLine()}, the only change needed is to take the same actions as when in the O state as in the S state. For the cache access statistics there is no need for change. \textcolor{red}{One additional change needed to the MESI protocol is that when a cache line is in the O state and gets replaced the owner ship must be returned to the memory.}

\textcolor{red}{We assume that the next level cache, the LLC, does not implement any CCP as there is no other caches on the same level that needs to be synchronized with. Because of this, change of ownership is not explicitly performed in any of the \textit{readLine(), writeLine(), readRemoteAction(), or writeRemoteAction()} functions. This as, when the line gets replaced, the state information gets overwritten with the replacing line's state information.}

>>>>

\subsection{Task 4}
To add the Owner (O) state to the existing MESI CCP, only small changes are needed. In \textit{readLine()} and \textit{writeRemoteAction()} no changes are needed. Turning to \textit{readRemoteAction()}, transitions from the E, M, and O states to the O state are added, and all of these transitions provide data to the calling cache. The action taken when in the shared state is removed. For \textit{writeLine()}, the only change needed is to take the same actions as when in the O state as in the S state. For the cache access statistics there is no need for change. \textcolor{red}{One additional change needed to the MESI protocol is that when a cache line in the O state gets replaced, the ownership must be returned to the memory. The change of ownership is not explicitly performed in any of the \textit{readLine(), writeLine(), readRemoteAction(), or writeRemoteAction()} functions. This as, when the line gets replaced, the state information is overwritten with the replacing line's state information, and thus is the ownership transferred to the LLC.}
